Automated Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-02 paper.tex
minor fixes
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Given a class of CPS's $\Omega$ and a set $\Phi$ of desired properties, a class of verification problems is called decidable, if there is an algorithm that is able to decide in a finite number of steps whether $\forall \mathcal{O}\in\Omega$ satisfies every property $\mathcal{L}\in \Phi$~\cite{Alur00}. Decidability is a key issue in CPS verification, since there are uncountable states and complex dynamics to be considered, {\it i.e.}, hybrid automata and their variations (usually employed to model CPS) are infinite-state machines~\cite{Henzinger95}. Generally, the properties that must be hold for CPS are related to safety, liveness, and reachability. In particular, model checking procedures have been employed to verify these properties of model programs even under undecidability conditions via approximations, {\it e.g.} bounding the number of steps from the initial state, which leads to bounded model checking~\cite{Veanes09}.

In addition, Shoukry {\it et. al} \cite{Shoukry} tackled another important problem related to CPSs: security. Indeed, the essence of CPSs claims for sophisticated interfacing ({\it e.g.}, sensors and network connections), which normally leads to security issues~\cite{cpsattack}, given that wrong control actions can be generated through corrupted measurements. The mentioned authors proposed a methodology for estimating the state of physical systems, through formal methods, even if sensor inputs are contaminated with erroneous or intentionally corrupted data, in order to still be able to execute suitable control commands. Indeed, many situations can be regarded as satisfiability problems and solved, for instance, with approaches based on Satisfiability Modulo Theories (SMT)~\cite{Araujo16} \textcolor{red}{eh bom citar mais fontes}, which indicates many links with other research areas and might lead to a unified approach regarding system verification, security enforcement, and interaction handling.

>>>>

Given a class of CPS's $\Omega$ and a set $\Phi$ of desired properties, a class of verification problems is called decidable, if there is an algorithm that is able to decide in a finite number of steps whether $\forall \mathcal{O}\in\Omega$ satisfies every property $\mathcal{L}\in \Phi$~\cite{Alur00}. Decidability is a key issue in CPS verification, since there are uncountable states and complex dynamics to be considered, {\it i.e.}, hybrid automata and their variations (usually employed to model CPS) are infinite-state machines~\cite{Henzinger95}. Generally, the properties that must be hold for CPS are related to safety, liveness, and reachability. In particular, model checking procedures have been employed to verify these properties of model programs even under undecidability conditions via approximations, {\it e.g.}, bounding the number of steps from the initial state, which leads to bounded model checking~\cite{Veanes09}.

In addition, Shoukry {\it et al.} \cite{Shoukry} tackled another important problem related to CPSs: security. Indeed, the essence of CPSs claims for sophisticated interfacing ({\it e.g.}, sensors and network connections), which normally leads to security issues~\cite{cpsattack}, given that wrong control actions can be generated through corrupted measurements. The mentioned authors proposed a methodology for estimating the state of physical systems, through formal methods, even if sensor inputs are contaminated with erroneous or intentionally corrupted data, in order to still be able to execute suitable control commands. Indeed, many situations can be regarded as satisfiability problems and solved, for instance, with approaches based on Satisfiability Modulo Theories (SMT)~\cite{Araujo16} \textcolor{red}{eh bom citar mais fontes}, which indicates many links with other research areas and might lead to a unified approach regarding system verification, security enforcement, and interaction handling.
